---
title: "Homework 1"
author: Alexey Abramov
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
---

# Setup
```{r}
library(tidyverse)
library(ggplot2)
```

# Module 1
## Problem 1

### Read in data and perform calculations

```{r, results='markup'}
problem1_df = 
  tibble(
    women_sample = c(1:11),
    fe_level = c(15.2, 9.3, 7.6, 11.9, 10.4, 9.7, 20.4, 9.4, 11.5, 9.4, 8.3)
    )
fivenum(c(15.2, 9.3, 7.6, 11.9, 10.4, 9.7, 20.4, 9.4, 11.5, 9.4, 8.3))
mean(c(15.2, 9.3, 7.6, 11.9, 10.4, 9.7, 20.4, 9.4, 11.5, 9.4, 8.3))
var(problem1_df$fe_level)

sd(problem1_df$fe_level)

```

## Problem 2

### Work shown in Word document

## Problem 3

### Importing Data
```{r}
problem3_df = read_table("./data/Pacemaker.txt")
```

### Create a histogram
```{r}
hist(problem3_df$Time, col = "lightblue", main = "Pacemaker Data", xlab = "Time in Months")
```

### Calculate the mean, median, variance and standard deviation.

```{r}
mean(problem3_df$Time)
median(problem3_df$Time)
var(problem3_df$Time)
sd(problem3_df$Time)
```

### Calculate range

```{r}
range(problem3_df$Time)
```

## Problem 4

### Read in data and create a boxplot
```{r}
problem4_df = read_table2("./data/BloodPressure.txt")

ggplot(problem4_df, aes(x= Race, y= BP, fill = Race)) + 
  geom_boxplot(fill="lightblue")+
  labs(title="Blood Lead Levels", x="Race", y = "Blood Lead Level (micrograms per deciliter)")+
  theme_classic()
```

## Problem 5

### Create a random distribution with 20 test scores with mean = 250, sd = 50.  
```{r}
set.seed(124)
problem5_df = 
  tibble(
    student = 1:20,
    testscore = rnorm(20, 250, 50)
  )
mean1 = mean(problem5_df$testscore)
mean1

var1 = var(problem5_df$testscore)
var1
```

### Now increase the test scores by 25% and calculate the new variance.

```{r}
problem5_df_2 = problem5_df$testscore*1.25
mean2 = mean(problem5_df_2)
mean2

var2 = var(problem5_df_2)
var2
```

### Calculations, ?change in mean and variance.

```{r}
change_in_mean = mean2 / mean1
change_in_mean

change_in_var = var2 / var1
change_in_var
```

# Module 2
## Problem 7

### Calculations shown
```{r}
problem7_df = c(60, 30, 5, 1, 78, 16, 3, 2, 86, 10, 2, 1)
p7_total = sum(problem7_df)
(78+16+3+2) / p7_total *100
(60 + 78 + 86) / 294
(60+ 30+ 5+ 1) / 294
```

# Module 3

## Binomial distributions

### Tutorial
To obtain a binomial probability for a single X value: 
dbinom(x, n, p) 
So for Example 1, we have: dbinom(0, 5, 0.15) 

To obtain a probability for values less than or equal to X:
pbinom(x, n, p) 
So for Example 2, we have: pbinom(2, 5, 0.15)

## Problem 9

```{r}

```

